Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-26 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical  Systems  (CPS)  are  “engineered systems  that  are built from, and depend upon, the seamless integration of computational  and  physical  components”~\cite{NSF2015}. During operation, such components must frequently adapt to the executing environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].

@@

In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools, e.g. PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}. However, those tools are based on simulation models; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

@@

\textcolor{red}{The main contributions of this approach is (1) to address a CPS, allowing that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the system together with user requirements and environment constraints, and the algorithm using automated verification, written in language C, can find the best compromise between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; and (2), to evaluate different state-of-art software verifiers in order to obtain the better performance. The use of automated verication in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.}
%
%\textcolor{red}{We need to make our contributions stronger. Why the SE community would be interested in this paper? What are the main open problems we need them to solve here? Remember that this is a paper for new ideas... we don't need to make questions but we don't need to answer all of them.}
%
%, using non-deterministic variables and exploring the design-space
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t. user requirements.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CBMC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}. CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{ESBMC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end based on clang that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; (iii) \textcolor{red}{we should describe the symbolic execution with incremental solving phase here...} and finally (iv) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. 
%ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. 
%This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Ultimate Automizer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties. The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement (CEGAR) scheme. CEGAR is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check and refinement~\cite{CEGAR}. In each iteration, Automizer picks a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible. If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility. The predicates are a sequence of interpolants since each predicate "interpolates" between a set of reachable states and a set of states from which it cannot reach the error. In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed. It is used automata to represent sets of traces. The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}. 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CPAchecker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Automatic program verification requires a choice between precision and efficiency. The
more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was
reflected in two major approaches to static verification: program analysis and model
checking. In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). For night hours or rainy days, we need to hold batteries where power can be stored and used. The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{blockdiagramPVS2}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
\\

@@

The sizing project check of the inverter is carried out by means of three equations. Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$). Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}
% -------------------------------------------------------
\section{Optimum sizing of PV systems}
% -------------------------------------------------------
To select an optimum combination of compontntes from a PV system in order to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}.

@@

However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC). Here, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.

%------------------------------------------------------
\section{Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------

@@

\textcolor{red}{The main challenge for the verification part is to found a feasible solution (technically speaking, regarding the constraints and user requirements) that is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is inputted to the tool}.

%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------

We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical  Systems  (CPS)  are  “engineered systems  that  are built from, and depend upon, the seamless integration of computational  and  physical  components”~\cite{NSF2015}. During operation, such components must frequently adapt to the executing environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].

@@

In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, those tools are based on simulation models; it has the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

@@

\textcolor{red}{The main contributions of this approach is (1) to address a CPS, allowing that a list of PV components (PV panels, charge controllers, inverters and batteries) can be inputted to the proposed tool together with user requirements and environment constraints, and the algorithm using automated verification (written in language C), can find the best compromise between two objectives: power reliability and system cost, i.e., linking the optimum solution in technical and economical terms; and (2), to evaluate different state-of-art software verifiers in order to obtain the better performance. The use of automated verication in electrical systems was uncommon in prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented.}
%
%\textcolor{red}{We need to make our contributions stronger. Why the SE community would be interested in this paper? What are the main open problems we need them to solve here? Remember that this is a paper for new ideas... we don't need to make questions but we don't need to answer all of them.}
%
%, using non-deterministic variables and exploring the design-space
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Automated Verification}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t. user requirements.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CBMC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}. CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{ESBMC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end based on clang that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; (iii) \textcolor{red}{we should describe the symbolic execution with incremental solving phase here...} and finally (iv) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. 
%ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. 
%This technique is called "incremental SMT"~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Ultimate Automizer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties. The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement (CEGAR) scheme. CEGAR is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check and refinement~\cite{CEGAR}. In each iteration, Automizer picks a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible. If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility. The predicates are a sequence of interpolants since each predicate "interpolates" between a set of reachable states and a set of states from which it cannot reach the error. In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed. It is used automata to represent sets of traces. The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}. 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CPAchecker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Automatic program verification requires a choice between precision and efficiency. The
more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was
reflected in two major approaches to static verification: program analysis and model
checking. In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). For night hours or rainy days, we need to hold batteries where power can be stored and used. The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{blockdiagramPVS2}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
\\

@@

The sizing project check of the inverter is carried out by means of three equations. Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$). Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}
% -------------------------------------------------------
\subsection{Optimum sizing of PV systems}
% -------------------------------------------------------
To select an optimum combination of compontntes from a PV system in order to meet sizing constraints, we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system is made by the best compromise between those two objectives (power reliability and system cost)~\cite{Alsadi2018}.

@@

However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC). Here, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
%------------------------------------------------------
\section{APPLYING AUTOMATED VERIFICATION TO OPTIMAL SIZING OF STAND-ALONE PV SYSTEMS}
%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------

@@

\textcolor{red}{The main challenge for the verification part is to found a feasible solution (technically speaking, regarding the constraints and user requirements) that is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is inputted to the tool}.
%---------------------------------------------------------------------------
\section{RESULTS AND DISCUSSION}
%---------------------------------------------------------------------------
We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.
